Active-contours driven registration of diffusion MR images of the brain

### 2015-03-16 Publications/2015-NeuroImage/06-discussion.tex
add potential applications to discussion

The hypothesis underpinning our research is that image registration can be reliably performed
  by searching for homogeneous regions in the target image that correspond to precise contours
  from an atlas, or extracted from other image (i.e. a different time step).

We designed \emph{regseg} as a method to correct \gls*{dmri} data for susceptibility
  distortions.
Connectome extraction protocols generally include the acquisition of \gls*{t1} images
  to provide with prior information about anatomy with high accuracy.
Our method solves in one single step a joint problem usually addressed in two steps:
  linear registration of \gls*{t1} and \gls*{dmri} to fuse the anatomical information on
  the diffusion data, and distortions correction using extra acquisitions.
Moreover, our method does not require any additional acquisition over the minimal protocol
  that only includes \gls*{t1} and \gls*{dmri} images, a very common scenario for
  historical datasets.

>>>>

The hypothesis underpinning our research is that image registration can be reliably performed
  by searching for homogeneous regions in the target image that correspond to precise contours
  from an atlas, or extracted from other image (i.e. a different time step).
We designed \emph{regseg} as a method to correct \gls*{dmri} data for susceptibility
  distortions.
Applications of whole-brain tractography generally include the acquisition of \gls*{t1} images
  to provide with prior information about anatomy with high accuracy.
Our method solves in one single step a joint problem usually addressed in two steps:
  linear registration of \gls*{t1} and \gls*{dmri} to fuse the anatomical information on
  the diffusion data, and distortions correction using extra acquisitions.
Moreover, our method does not require any additional acquisition over the minimal protocol
  that only includes \gls*{t1} and \gls*{dmri} images, a very common situation for
  historical datasets.
Beyond the proposed correction, potential applications of \emph{regseg} are atlas-based
  segmentation and tracking objects in time-series.
